\documentclass[letterpaper,10.5pt]{article}

\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\input{glyphtounicode}

% Page + spacing control
\linespread{0.98}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.0in}
\addtolength{\topmargin}{-0.65in}
\addtolength{\textheight}{1.32in}

\raggedright
\raggedbottom
\setlength{\tabcolsep}{0in}
\pdfgentounicode=1

% Section formatting (clean)
\titleformat{\section}
  {\vspace{-2pt}\scshape\raggedright\large\bfseries}
  {}{0em}{}[\titlerule \vspace{-3pt}]

% Commands
\newcommand{\resumeItem}[1]{\item\small{#1}}
\newcommand{\resumeSubheading}[4]{
\item
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
\textbf{#1} & \textbf{\small #2} \\
\textit{\small #3} & \textit{\small #4} \\
\end{tabular*}
}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0in, label={}, itemsep=4pt]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=0.25in, itemsep=2pt]}
\newcommand{\resumeItemListEnd}{\end{itemize}}

%-------------------------------------------
\begin{document}

% HEADER
\begin{center}
{\Huge \scshape Uppu Vamsi}\\
DOB: 14 Oct 2003 \quad Vivek Nagar, North 24 Paraganas, West Bengal\\
\small
\faPhone\ (+91) 8274995480 \quad
\href{mailto:vamsiuppu4@gmail.com}{\faEnvelope\ vamsiuppu4@gmail.com} \quad
\href{https://github.com/SamXavii902}{\faGithub\ github.com/SamXavii902}
\end{center}

% EDUCATION
\section{Education}
\resumeSubHeadingListStart
\resumeSubheading
{National Institute of Technology, Rourkela}{Aug 2025 -- Present}
{M.Tech in Signal and Image Processing}{Rourkela, Odisha}
\resumeSubheading
{National Institute of Technology, Srinagar}{Jun 2021 -- Jul 2025}
{B.Tech in Information Technology (CGPA: 6.742)}{Srinagar, J\&K}
\resumeSubheading
{Sri Chaitanya Jr. College}{May 2021}
{BIEAP (PCM) -- 90.5\%}{Vishakhapatnam, AP}
\resumeSubheading
{Vijnana Vihara Residential School}{May 2019}
{CBSE AISSE -- 93\%}{Vishakhapatnam, AP}
\resumeSubHeadingListEnd

% COURSEWORK
\section{Relevant Coursework}
\begin{multicols}{2}
\begin{itemize}[itemsep=1pt]
\item Data Structures and Algorithms
\item Design and Analysis of Algorithms
\item Database Management Systems
\item Operating Systems
\item Computer Networks
\item Object Oriented Programming
\end{itemize}
\end{multicols}

% PROJECTS
\section{Projects}
\resumeSubHeadingListStart

\resumeSubheading
{Secure Steganography-Based Messaging Platform}{Jan 2026 -- Present}
{Kotlin, Jetpack Compose, Python (Chaquopy), FastAPI, MongoDB, Socket.IO}{}
\resumeItemListStart
\resumeItem{Engineered a real-time secure messaging app using a \textbf{hybrid Native/Python architecture}, integrating \textbf{Chaquopy} to execute complex PVD steganography and cryptography scripts directly within the Android runtime.}
\resumeItem{Implemented \textbf{End-to-End Encryption} using \textbf{ECDH key exchange} and \textbf{ChaCha20-Poly1305}, creating and securing shared secrets via the hardware-backed \textbf{Android KeyStore}.}
\resumeItem{Designed a low-latency bi-directional event system with \textbf{Socket.IO} to handle instant message delivery, offline synchronization, and reliable read receipts.}
\resumeItem{Developed a scalable \textbf{FastAPI} backend with \textbf{MongoDB} for user/metadata management and integrated \textbf{Cloudinary} for lossless image storage services.}
\resumeItem{Optimized payload efficiency using \textbf{LZ4 compression} and reduced statistical detectability via randomized **Magic Matrix** embedding.}
\resumeItemListEnd

\resumeSubheading
{Advanced Hybrid Steganography \& Cryptography Suite}{Jan 2025 -- Apr 2025}
{Python, OpenCV, NumPy, Cryptography}{}
\resumeItemListStart
\resumeItem{Developed the core steganographic engine combining \textbf{Pixel Value Differencing (PVD)} and randomized \textbf{Magic Matrix} techniques for high-capacity, invisible data hiding.}
\resumeItem{Conducted automated security analysis using Entropy, Histogram, and PSNR/SSIM metrics to rigorously validate image quality and imperceptibility.}
\resumeItemListEnd

\resumeSubheading
{Additional Technical Projects}{}{}{}
\resumeItemListStart
\resumeItem{\textbf{Touchless Interface}: Real-time gesture control system for HCI using OpenCV and MediaPipe hand tracking.}
\resumeItem{\textbf{Robot Tracker}: Dynamic object tracking system implementing hybrid CSRT + Extended Kalman Filter.}
\resumeItem{\textbf{IntelliPass-Hybrid-AI}: Password strength analyzer using Multi-Layer Perceptrons (MLP) and fuzzy logic.}
\resumeItemListEnd

\resumeSubHeadingListEnd

% SKILLS
\section{Technical Skills}
\begin{itemize}[leftmargin=0.25in, itemsep=2pt]
\item \textbf{Languages}: Python, Kotlin, C, MATLAB, SQL, HTML/CSS
\item \textbf{Core Domains}: Image Processing, Computer Vision, Applied Cryptography, Android Development, HCI
\item \textbf{Frameworks \& Tools}: Jetpack Compose, FastAPI, OpenCV, MediaPipe, Git, Docker, Linux, Figma
\end{itemize}

\end{document}
